---
title: "bariatric_2"
author: "Dan Gunn"
---

## Bariatric Suppliers vs. Junk Food Companies vs. Ozempic

```{r echo=FALSE}
library(lubridate)
library(tidyquant)
library(tidyverse)
library(ggtext)
library(showtext)
```

The Bariatric Surgery Supplier companies are...

| Company              | Exchange | Ticker |
|----------------------|----------|--------|
| Johnson & Johnson    | NYSE     | JNJ    |
| Medtronic            | NYSE     | MDT    |
| Olympus Corporation  | NYSE     | OCPNF  |
| Boston Scientific    | NYSE     | BSX    |
| Asensus Surgical     | NYSE     | ASXC   |
| ConMed Corporation   | NASDAQ   | CNMD   |
| Intuitive Surgical   | NASDAQ   | ISRG   |
| Apollo Endosurgery   | Delisted | APEN   |
| ReShape Lifesciences | NASDAQ   | RSLS   |

```{r}
symbol_list <- c("JNJ", "MDT", "OCPNF", "BSX", "ASXC", "CNMD", "ISRG", "RSLS")
start_date <- "2020-01-01"  # Example start date
end_date <- "2023-12-31"    # Example end date

bariatric_stock_prices <- tq_get(symbol_list, 
                       from = start_date, 
                       to = end_date, 
                       get = "stock.prices",
                       collapse="monthly")
```

The processed (junk) food companies will be...

| Company                | Exchange | Ticker |
|------------------------|----------|--------|
| Pespico                | NASDAQ   | PEP    |
| Nestlé USA             |          | NSRGY  |
| Kraft Heinz Company    | NASDAQ   | KHC    |
| General Mills          | NYSE     | GIS    |
| Mondelez International | NASDAQ   | MDLZ   |
| Kellogg Company        | NYSE     | K      |
| Conagra Brands         | NYSE     | CAG    |
| Campbell Soup Company  | NYSE     | CPB    |
| J.M. Smucker Company   | NYSE     | SJM    |

```{r}
symbol_list_2 <- c("PEP", "NSRGY", "KHC", "GIS", "MDLZ", "K", "CAG", "CPB", "SJM")

junkfood_stock_prices <- tq_get(symbol_list_2, 
                       from = start_date, 
                       to = end_date, 
                       get = "stock.prices",
                       collapse="monthly")
```

There's only one maker of Ozempic at the moment.

| Company      | Exchange | Ticker |
|--------------|----------|--------|
| Novo Nordisk | NYSE     | NVO    |
| Eli Lilly    | NYSE     | LLY    |

```{r}
symbol_list_3 <- c("NVO", "LLY")

pharma_stock_prices <- tq_get(symbol_list_3, 
                       from = start_date, 
                       to = end_date, 
                       get = "stock.prices",
                       collapse="monthly")
```

What if it's just Novo Nordisk

```{r}
symbol_list_4 <- c("NVO")

novo_stock_prices <- tq_get(symbol_list_4, 
                       from = start_date, 
                       to = end_date, 
                       get = "stock.prices",
                       collapse="monthly")
```

```{r}
library(viridis)
library(viridisLite)

hex_codes <- viridis(n = 5, option = "G") # Adjust 'n' for the number of colors you need
hex_codes

```

Combine each data set into daily averages....

```{r}
bariatric_daily_average <- bariatric_stock_prices %>%
  group_by(date) %>%
  summarize(Average_Adjusted = mean(adjusted, na.rm = TRUE))
```

```{r}
junkfood_daily_average <- junkfood_stock_prices %>%
  group_by(date) %>%
  summarize(Average_Adjusted = mean(adjusted, na.rm = TRUE))
```

```{r}
pharma_daily_average <- pharma_stock_prices %>%
  group_by(date) %>%
  summarize(Average_Adjusted = mean(adjusted, na.rm = TRUE))
```

```{r}
font_add_google(name = "Lato", family = "lato")

showtext_auto()
```

Now I'm going to plot it to see what's going on.

```{r}
ggplot() +
    geom_area(data=bariatric_daily_average,
            aes(x=date, y= Average_Adjusted),
            color = "#399687",
             fill= "#399687",
            alpha = 0.3)+
    geom_area(data=junkfood_daily_average,
            aes(x=date, y= Average_Adjusted),
            color = "#3E356BFF",
            fill= "#3E356BFF",
            alpha = 0.3)+
  geom_area(data=novo_stock_prices,
            aes(x=date, y= adjusted),
            color = "#FF3F70",
            fill = "#FF3F70",
            alpha = 0.3)+
  geom_vline(xintercept = as.Date("2021-06-04"), 
             linetype = "dotted", 
             color = "#FF3F70",
             size = 1)+ 
  scale_x_date(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0),
                     labels = scales::label_dollar())+
  labs(#title ="Ozempic vs. Junkfood vs. Bariatrics",
       #subtitle = "Percentage change since Jan 1 2020",
       #caption="Ozempic FDA Approval Date for Weigh Loss Highlighed",
       y=NULL,
       x= NULL)+
  theme_minimal()+
  theme(axis.text = element_text(family ="lato", face="bold", size =10, color = "#3E356BFF"),
        panel.grid.minor = element_blank(),
        axis.line= element_line(color = "#3E356BFF", linewidth = 0.25),
        axis.ticks = element_blank()
        )

```

```{r}
ggsave(filename =  "charts/bariatric_2_stock.pdf", 
       plot = last_plot(), 
       device = "pdf", 
       dpi= 400,
       height =4,
       width = 6)
```

Now I'd like to plot percentage change up and down.

```{r}
# Calculate percentage change
b_initial_value <- bariatric_daily_average$Average_Adjusted[1]
j_initial_value <- junkfood_daily_average$Average_Adjusted[1]
n_initial_value <- novo_stock_prices$adjusted[1]

bariatric_daily_average <- bariatric_daily_average %>%
  mutate(perc_change = ((Average_Adjusted - b_initial_value) / b_initial_value) * 100)
 
junkfood_daily_average <- junkfood_daily_average %>% 
  mutate(perc_change = ((Average_Adjusted - j_initial_value) / j_initial_value) * 100)

novo_stock_prices<- novo_stock_prices %>% 
  mutate(perc_change = ((adjusted- n_initial_value) / n_initial_value) * 100)

```

```{r}
#writing to CSV
write_csv(bariatric_daily_average, "clean_data/bariatric_daily_average.csv")
write_csv(junkfood_daily_average, "clean_data/junkfood_daily_average.csv")
write_csv(novo_stock_prices, "clean_data/novo_stock_prices.csv")

#left joining to use with Datylon
data_combined <- bariatric_daily_average %>% rename(b_perc_change = perc_change,
                                   b_Average_Adjusted= Average_Adjusted) %>%
  left_join(junkfood_daily_average, by = join_by(date))%>%
  rename(j_perc_change = perc_change,
         j_Average_Adjusted= Average_Adjusted)%>%
  left_join(novo_stock_prices, by = join_by(date))


write_csv(data_combined, "clean_data/datacombined.csv")
```

```{r}
# Plot centered around zero
ggplot() +
    geom_area(data=novo_stock_prices,
            aes(x=date, y= perc_change),
            color = "#FF3F70",
            fill = "#FF3F70",
            alpha = 0.3)+

  geom_area(data=junkfood_daily_average,
            aes(x=date, y= perc_change),
            color = "#3E356BFF",
            fill= "#3E356BFF",
            alpha = 0.3)+
    geom_area(data=bariatric_daily_average,
            aes(x=date, y= perc_change),
            color = "#399687",
            fill = "#399687",
            alpha = 0.3)+

  geom_vline(xintercept = as.Date("2021-06-04"), 
             linetype = "dotted", 
             color = "#FF3F70",
             linewidth = 0.75) +
  scale_x_date(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0),
                     labels = scales::label_percent(scale = 1))+
  labs(#title ="Ozempic vs. Junkfood vs. Bariatrics",
       #subtitle = "Percentage change since Jan 1 2020",
       #caption="Ozempic FDA Approval Date for Weigh Loss Highlighed",
       y=NULL,
       x= NULL)+
  theme_minimal()+
  theme(axis.text = element_text(family ="lato", face="bold", size =10, color = "#3E356BFF"),
        panel.grid.minor = element_blank(),
        axis.line= element_line(color = "#3E356BFF", linewidth = 0.25),
        axis.ticks = element_blank()
        )
```

```{r}
ggsave(filename =  "charts/bariatric_2_percent.pdf", 
       plot = last_plot(), 
       device = "pdf", 
       dpi= 400,
       height=4,
       width=6)
```

**Methodology:** Adjusted stock prices gathered from January 1, 2020 to December 31, 2023. Surgery manufacturers included the average price of Johnson & Johnson, Medtronic, Olympus, Boston Scientific, Asensus Surgical, ConMed, Intuitive Surgical**,** Apollo Endosurgery and ReShape Lifesciences. Processed food corporations included the average price of PepsiCo, Nestlé, Kraft Heinz, General Mills, Mondelez, Kellogg, Conagra, Campbell Soup and J.M. Smucker.

**Source:** Yahoo Finance

Exported to Adobe Illustrator for completing the infographic.
